Developing a Bubble Chamber Particle Discriminator Using Semi-Supervised Learning

### 2018-08-13 documentation/paper.tex
Added histogram for waveform with wall cut

\begin{figure}[h]
    \centering
    \includegraphics[width=\textwidth]{waveform_hist}
    \caption{\label{waveform_hist} Prediction distribution of the best $DeepConvWithPos(\omega, \chi)$ discriminator.}
\end{figure}

When $WallCut(D)$ was included, both accuracy and class-wise standard deviation improved drastically. The best configuration during a grid search was 96\% accurate and had a standard deviation of 0.41. This is better by both metrics than the multi-layer perceptron used in the original PICO-60 analysis.

>>>>

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{waveform_hist}
    \caption{\label{waveform_hist} Prediction distribution of the best $DeepConvWithPos(\omega, \chi)$ discriminator without $WallCut(D)$.}
\end{figure}

When $WallCut(D)$ was included, both accuracy and class-wise standard deviation improved drastically. The best configuration during a grid search was 96\% accurate and had a standard deviation of 0.41 (seen in Figure \ref{waveform_wall_cut_hist}). This is better by both metrics than the multi-layer perceptron used in the original PICO-60 analysis.

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{waveform_wall_cut_hist}
    \caption{\label{waveform_wall_cut_hist} Prediction distribution of the best $DeepConvWithPos(\omega, \chi)$ discriminator with $WallCut(D)$.}
\end{figure}
